noam_data_exploration_v1

### 2024-07-17 noam_data_exploration_v3.Rmd
Rearranged a couple chunks

@@

```{r gam approach}
# NOTE: Not sure where I'm going with this yet
# Idea is to look at smoother estimates for each time series to get an idea for the "shape" of the time series
# Not sure if worthwhile, might skip

# same workflow as above
for(i in 1:length(unique(alpha_diversity_quad$Location)) ){ # for each  quadrat
  # create a new dataframe for the quadrat of the current iteration
  newData <- subset(alpha_diversity_quad, Location == levels(alpha_diversity_quad$Location)[i])

>>>>

```
```{r gam approach}
# NOTE: Not sure where I'm going with this yet
# Idea is to look at smoother estimates for each time series to get an idea for the "shape" of the time series
# Not sure if worthwhile, might skip

# same workflow as *below (I did gls first originally)
for(i in 1:length(unique(alpha_diversity_quad$Location)) ){ # for each  quadrat
  # create a new dataframe for the quadrat of the current iteration
  newData <- subset(alpha_diversity_quad, Location == levels(alpha_diversity_quad$Location)[i])

@@
